% =============================================================
% Aalok Thakkar - Curriculum Vitae (minimal academic version)
% Compile with: pdflatex aalok_cv.tex (twice for headers).
% Format adapted from a Pei-Wu-style academic CV (running page
% header, small-caps section labels, two-column hanging entries).
% =============================================================
\documentclass[11pt,letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in,top=0.9in,bottom=1in]{geometry}
\usepackage{microtype}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{array}
\usepackage{hyperref}
\usepackage{parskip}

\hypersetup{
  colorlinks=true,
  linkcolor=black,
  citecolor=black,
  filecolor=black,
  urlcolor=black,
  pdftitle={Aalok Thakkar - Curriculum Vitae},
  pdfauthor={Aalok Thakkar}
}

% ---------------- Running page header --------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[C]{\small\textsc{Aalok Thakkar} \, $\bullet$ \, \textsc{Curriculum Vitae} \, $\bullet$ \, 2026}
\fancyfoot[C]{\small\thepage}

% ---------------- Section headings -----------------------
% Replace \section's formatting without titlesec.
\makeatletter
\renewcommand{\section}{\@startsection{section}{1}{0pt}%
  {1.6em}%      space before
  {0.6em}%      space after
  {\normalfont\large\bfseries}%
}
\makeatother
% Append a rule under each section title via \cvsection wrapper.
\newcommand{\cvsection}[1]{%
  \section*{#1}\vspace{-0.6em}\noindent\rule{\linewidth}{0.4pt}\vspace{0.2em}\par
}
% Lighter sub-heading
\newcommand{\cvsubsection}[1]{\vspace{0.5em}\noindent{\normalsize\itshape #1}\par\vspace{0.2em}}

% ---------------- Two-column entry helper ----------------
% Usage: \entry{LEFT DATE COLUMN}{RIGHT CONTENT}
\newcommand{\entry}[2]{%
  \noindent
  \begin{minipage}[t]{0.18\linewidth}\raggedright\small\textsc{#1}\end{minipage}%
  \hspace{0.02\linewidth}%
  \begin{minipage}[t]{0.78\linewidth}#2\end{minipage}\par\vspace{0.6em}
}

% Publication entry: title, authors, venue.
\newcommand{\pub}[3]{%
  \noindent\textbf{#1}\\
  \small #2\\
  \itshape #3\par\vspace{0.5em}
}

% =============================================================
\begin{document}
\thispagestyle{fancy}

% ---------------- Academic Appointment -------------------
\cvsection{Academic Appointment}

\entry{2024--present}{%
  \textsc{Ashoka University}, Sonipat, India \\
  Department of Computer Science \\
  \emph{Assistant Professor}}

% ---------------- Education ------------------------------
\cvsection{Education}

\entry{2018--2023}{%
  \textsc{University of Pennsylvania} \\
  Ph.D., Computer and Information Science \\
  Thesis: \emph{Example-Guided Synthesis of Relational Queries} \\
  Advisors: Rajeev Alur and Mayur Naik}

\entry{2015--2018}{%
  \textsc{Chennai Mathematical Institute} \\
  B.Sc.~(Honours), Mathematics and Computer Science}

% ---------------- Publications ---------------------------
\cvsection{Selected Publications}

\cvsubsection{Conference Publications}

\pub{A Correctness-First Introduction to Computer Science}
  {with Vaani Goenka}
  {Innovation and Technology in Computer Science Education (ITiCSE 2026)}

\pub{A Good Rubber Duck Does Not Quack}
  {with Ayush Thonge}
  {Innovation and Technology in Computer Science Education (ITiCSE 2026)}

\pub{Mobius: Synthesizing Relational Queries with Recursive and Invented Predicates}
  {with Nathaniel Sands, George Petrou, Rajeev Alur, Mayur Naik, and Mukund Raghothaman}
  {Object-Oriented Programming, Systems, Languages, and Applications (OOPSLA 2023)}

\pub{Relational Query Synthesis $\bowtie$ Decision Tree Learning}
  {with Aaditya Naik, Adam Stein, Rajeev Alur, and Mayur Naik}
  {International Conference on Very Large Data Bases (VLDB 2023)}

\pub{Example-Guided Synthesis of Relational Queries}
  {with Aaditya Naik, Nathaniel Sands, Mukund Raghothaman, Mayur Naik, and Rajeev Alur}
  {Programming Language Design and Implementation (PLDI 2021)}

\cvsubsection{Journal Publications}

\pub{Reopening businesses and risk of COVID-19 transmission}
  {with Ashley O'Donoghue, Tenzin Dechen, Whitney Pavlova, Michael Boals, Garba Moussa, Manvi Madan, Frank J.~DeFalco, and Jennifer P.~Stevens}
  {npj Digital Medicine 4, 51 (2021)}

\pub{Concurrency in Boolean networks}
  {with Thomas Chatain, Stefan Haar, Juraj Kolcak, and Loic Pauleve}
  {Natural Computing 19, 91--109 (2020)}

\pub{Infinitude of Primes Using Formal Languages}{}{The American Mathematical Monthly 125:8, 745--749 (2018)}

% ---------------- Teaching -------------------------------
\cvsection{Teaching}

\entry{Summer 2026}{FC-0306: Quantitative Reasoning and Mathematical Thinking}
\entry{Spring 2026}{CS-3330: Theory of Computation \\ CS-3610: Information Security}
\entry{Monsoon 2025}{CS-1102: Introduction to Computer Science \\ CS-5310: Symbolic Logic and Applications \\ CS-6101: Computer Science Research Methods and Seminars}
\entry{Summer 2025}{FC-0306: Quantitative Reasoning and Mathematical Thinking \\ CS-1102: Introduction to Computer Science}
\entry{Spring 2025}{CS-1102: Introduction to Computer Science \\ CS-5440: Trustworthy AI}
\entry{Monsoon 2024}{CS-5310: Symbolic Logic and Applications}

% ---------------- Grants ---------------------------------
\cvsection{Grants and Fellowships}

\entry{2026--}{%
  \textsc{ANRF Prime Minister Early Career Research Grant} \\
  Robust and scalable program synthesis.}

\entry{2025--2026}{%
  \textsc{Data \& AI Adoption Fellowship}, EkStep Foundation \\
  AI Safety Benchmarks for Education and Agriculture.}

\entry{2025--2026}{%
  \textsc{Darjeeling Revival Fellowship}, Alt Carbon \\
  Geostatistical modelling for enhanced rock weathering.}

\entry{2025--2026}{%
  \textsc{Adaptive and Inclusive Pedagogy Grant}, Mphasis \\
  Curriculum design for an adaptive and inclusive classroom.}

\entry{2026}{%
  \textsc{Nagarathna Memorial Grant} \\
  Translation of \emph{Nayi Kavita} poets into English.}

% ---------------- Service --------------------------------
\cvsection{Professional Service}

\entry{Organizer}{%
  Formal Methods Update Meeting 2026, Krea University. \\
  FSTTCS 2024, FSTTCS 2025. \\
  IARCS Verification Seminar Series. \\
  Logic Society of Delhi.}

\entry{Editor}{Corresponding editor, \emph{Bh\=avan\=a} magazine.}

\entry{Reviewer}{%
  Programme committees and review activities for POPL AEC 2022, ISEC 2025, PLDI SRC 2025, ATVA AEC 2025, OOPSLA 2026, and \emph{ACM Computing Surveys}.}

\entry{Memberships}{%
  Association for Computing Machinery (ACM India). \\
  Vijnana Bharati.}

\end{document}
